Paper Analysis

### 2025-05-01 Paper_WriteUp/Paper_Plots.qmd
better x-axis limits for RD/volatility plots

#RDs
RD_plot = ggplot(data = init_RDs %>% group_by(focal_user) %>% mutate(index = row_number()), mapping = aes(x = index, y = RD)) +
  geom_line() +
  scale_x_continuous(n.breaks = 3, limits = c(0, 10000)) +
  labs(x = "Game Number", y = "Rating Deviation") +
  facet_wrap(~focal_user)

@@

#volatilities
vol_plot = ggplot(data = init_RDs %>% group_by(focal_user) %>% mutate(index = row_number()), mapping = aes(x = index, y = volatility)) +
  geom_line() +
  scale_x_continuous(n.breaks = 3, limits = c(0, 10000)) +
  labs(x = "Game Number", y = "Rating Deviation") +
  facet_wrap(~focal_user)

>>>>

#RDs
RD_plot = ggplot(data = init_RDs %>% group_by(focal_user) %>% mutate(index = row_number()), mapping = aes(x = index, y = RD)) +
  geom_line() +
  scale_x_continuous(n.breaks = 3, limits = c(0, 5000)) +
  scale_y_continuous(limits = c(50, 100)) +
  labs(x = "Game Number", y = "Rating Deviation") +
  facet_wrap(~focal_user)

@@

#volatilities
vol_plot = ggplot(data = init_RDs %>% group_by(focal_user) %>% mutate(index = row_number()), mapping = aes(x = index, y = volatility)) +
  geom_line() +
  scale_x_continuous(n.breaks = 3, limits = c(0, 5000)) +
  #scale_y_continuous(limits = c(0.04, 0.06)) +
  labs(x = "Game Number", y = "Rating Deviation") +
  facet_wrap(~focal_user)
